Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-12 chapters/introduction/introduction.tex
minor change

@@

  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and on estimating the camera geo-orientation.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to the monocular depth
  estimation methods that driven by
  the technique called {\em Reprojection
  Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
  network learns to geometrically project pixels from the overhead
  images to the ground images,
  and learns to segment the overhead images jointly. 
  When refining the camera geographic location, we compare the
  semantic layout of the ground image with those transferred from
  overhead images sampled from different locations and orientations. The
  optimal prediction is found when the semantic layouts from these
  two sources match best. For probabilistic outputs, we assign
  a score to each location and orientation setting,
  based on how well the semantic layouts match to each other.
  We present the algorithm details in \chapref{crosstransf}
  \newline

@@

\section{Geo-Calibration for Feature Learning}

>>>>

\subsection{Geo-Calibration for Feature Learning}

Automatic feature engineering has drawn a lot of attention over the
past years in the computer vision community due to its efficiency and
not requiring expert knowledge about the data. Deep neural networks
are wildly accepted by researchers as good tools to learn high-level
image representations.
The most commonly used approach for deep image feature learning is
full supervision, which usually requires manually annotated data
\todo{citations}.
Though full supervision work well in many applications, there are
exponentially more image resources without manual annotations (cell
phone imagery, YouTube videos\etc), which show a huge potential for
visual feature learning.  In recent years, people start studying
various approaches to exploit those unlabeled data. 
%
Recent work has explored the use of self-supervision (sometimes
referred to as unsupervised learning or pretext tasks) for training
deep neural networks that capture useful visual
representations~\cite{doersch2015unsupervised,pathak2016context}. 
These methods typically
exploit some known quantity of the data (e.g., pixel color values) to
avoid expensive manual annotation. As a byproduct, a useful visual
representation is learned.
For example, Zhang et al.~\cite{zhang2016colorful} show how image
colorization (synthesizing colors for a grayscale image) is a powerful
pretext task for learning visual representations. Pathak et
al.~\cite{pathak2017learning} exploit low-level motion-based grouping
cues for unsupervised feature learning.  
%
As new learning technique address the lack of massive amounts of
labeled data, domain adaptation adapt the feature generating model to
another feature domain so that it improve the performance when dealing
with new input
data~\cite{fernando2013unsupervised,fernando2015joint,saenko2010adapting,wang2016actions,tinghui2016flow}.
Duan \etal~\cite{duan2012learning} proposed to learn a linear
projection to transfer from the source feature subspace to the target
subspace. Sohn \etal~\cite{sohn2017unsupervised} improved the
performance of video face recognition using an adversarial-based
approach to adapt the network to unlabled video imagery.

@@

  \item \textbf{Constraint for Fine Geographic Locations and Orientations:}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and on estimating the camera geo-orientation. 
  We first learn to segment the ground scene from its paired aerial image.
  When refining the camera geographic location, we compare the
  semantic layout of the ground image with those transferred from
  overhead images sampled from different locations and orientations. The
  optimal prediction is found when the semantic layouts from these
  two sources match best. For probabilistic outputs, we assign
  a score to each location and orientation setting,
  based on how well the semantic layouts match to each other.
  We present the algorithm details in \chapref{crosstransf}.
  \newline

@@

\subsection{Geo-Calibration for Feature Learning}
Our methods focus on lavaging the camera geographic information to
deal with the challenges of lacking manually annotated data during DNN
training. The insight is that the camera geographic information
encodes semantic information because it is related to the
appearances of the scenes.

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Feature Learning}
  Current machine learning methods address problems that involves mostly
  the ground-level imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery. In
  \chapref{crosstransf}, we proposed a method to learn aerial image
  semantic segmentation with ground-level ground truth. Our method
  exploits the spatial correspondences between images in cross-view
  pairs. 
  In this work, we try to transfer the semantics from the ground
  imagery to the overhead imagery by identifying the latent geometry
  correspondences between these two.  Similar to the monocular depth
  estimation methods that driven by the technique called {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
  network learns to geometrically project pixels from the overhead
  images to the ground images, and to segment the overhead images
  jointly.

  \item \textbf{Geo-Temporal Feature Learning}
  In our work, we consider two novel pretext
  tasks, time and location estimation. Our work is most similar to Li
  and Snavely~\cite{li2018learning}, who propose an approach for
  learning intrinsic images by observing image sequences with varying
  illumination over time. While their targets are reflectance and
  shading images of the scene, we focus on location and time.
\end{itemize}
